\documentclass{../local}
\renewcommand{\bibname}{Referenties}
\addcontentsline{toc}{chapter}{Bibliography}

\begin{document}

\begin{thebibliography}{9}

\bibitem{BarnesEmEv} Matthew Barnes, Hugh Leather, D. K. Arvind, \emph{Emergency Evacuation using Wireless Sensor Networks}, In Proceedings of IEEE International Conference on Local Computer Networks, 2007, pp. 851–857.

\bibitem{FireGrid}D. Berry, A. Usmani, J. Torero, et al, \emph{FireGrid: Integrated
emergency response and fire safety engineering for the future built environment}, In Workshop on
Ubiquitous Computing and e-Research. Edinburgh, UK: National eScience Centre.

\bibitem{ShaWSN} K. Sha, W. Shi, O. Watkins, \emph{Using Wireless Sensor Networks for Fire Rescue Applications: Requirements and Challenges}, In Proceedings of IEEE International Conference on Electro/information Technology, 2006, pp. 239-244.

\bibitem{StatRUP} T. Stathopoulos, J. Heidemann, D. Estrin, \emph{A remote code update mechanism for wireless sensor networks}, Technical report CENS-TR-30, USA, 2003.

\bibitem{NEMBES} NEMBES-Networked Embedded Systems,\\ http://www.ucc.ie/en/misl/research/previous/nembes

\bibitem{ZengFire} Y. Zeng, S. Murphy, L. Sitanayah, et al., \emph{Building Fire Emergency Detection and Response Using Wireless Sensor Networks}, In Proceedings of 9th Information Technology \&  Telecommunications Conference, Ireland, 2009.

\bibitem{ZengRTRR} Y. Zeng, C.J. Sreenan, L. Sitanayah, \emph{A Real-Time and Robust Routing Protocol for Building Fire Emergency Applications Using Wireless Sensor Networks}, 8th International Workshop on Real-Time Networks (RTN'09), 2009.

\bibitem{ZengERMAC} L. Sitanayah, C.J. Sreenan, K.N. Brown, \emph{ER-MAC: A hybrid MAC protocol for emergency response wireless sensor networks}, SENSORCOMM, Venice/Mestre, Italy, 2010, pp. 244-249. 

\end{thebibliography}

\end{document}